Entropy-SGD: Biasing Gradient Descent Into Wide Valleys

### 2017-01-11 doc/chaudhari.choromanska.ea.iclr17.tex

With some overload of notation, we assume that the original loss $f(x)$ is $\b$-smooth, i.e., for all $x,y \in \reals^n$, we have $\norm{\nabla f(x) - \nabla f(y)} \leq \b\ \norm{x-y}$. We additionally assume for the purpose of analysis that no eigenvalue of the Hessian $\nabla^2 f(x)$ lies in the set $[-2 \g-c, c]$ for some small $c > 0$.
%
\begin{lemma}
\label{lem:smoothness_reduction}
The objective $F(x, \g;\ \Xi)$ in~\eqref{eq:entropysgd_objective} is $\f{\a}{1 + \g^{-1}\ c}$-Lipschitz and $\f{\b}{1 + \g^{-1}\ c}$-smooth.
\end{lemma}
The local entropy objective is thus smoother than the original objective while the modified objective in~\eqref{eq:entropysgd_objective} results in a factor of $\r + \f{1}{1 + \g^{-1}\ c}$ in the above lemma.

@@

\section{Connection to variational inference}
\label{s:app:connection_variational}
The local entropy based objective in $\entropysgd$ has similar motivations as variational inference.

@@

>>>>

With some overload of notation, we assume that the original loss $f(x)$ is $\b$-smooth, i.e., for all $x,y \in \reals^n$, we have $\norm{\nabla f(x) - \nabla f(y)} \leq \b\ \norm{x-y}$. We additionally assume for the purpose of analysis that no eigenvalue of the Hessian $\nabla^2 f(x)$ lies in the set $[-2 \g-c, c]$ for some small $c > 0$.
%
\begin{lemma}
\label{lem:smoothness_reduction}
The objective $F(x, \g;\ \Xi)$ in~\eqref{eq:entropysgd_objective} is $\f{\a}{1 + \g^{-1}\ c}$-Lipschitz and $\f{\b}{1 + \g^{-1}\ c}$-smooth.
\end{lemma}
The local entropy objective is thus smoother than the original objective.

@@

@@

\subsection{Connection to variational inference}
\label{ss:connection_variational}
The local entropy based objective in $\entropysgd$ has similar motivations as variational inference.
